LAGOS lake depth

### 2020-03-25 figures/02_depth_model.Rmd
importance legend adjustments

```{r 02_depth_model_importance, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=3.5, fig.width=8}
dt_fits <- readRDS("../data/01_depth_model/depth_fits.rds")

@@

ggplot() + 
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +   
  # geom_hline(linetype = 3, size = 1, colour = "gray", 
  #                yintercept = 1:nlevels(dt$variable)) + 
  theme(text = element_text(family="Times"),
        panel.background = element_blank(), panel.grid = element_blank(),
        panel.border = element_rect(fill = NA), # legend.position = "none", 
        axis.title.x = element_text(family="sans", face = "bold", 
        vjust = -0.5, size = 12), 
        axis.text = element_text(family="sans",size = 11, 
                                 color = "black")) + 
        ylab("") + xlab("Percent Increase in Mean Square Error")
```

>>>>

```{r 02_depth_model_importance, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=3.5, fig.width=6}
dt_fits <- readRDS("../data/01_depth_model/depth_fits.rds")

@@

ggplot() + 
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +   
  labs(color = "slope-distance\nmeasure") +
  geom_hline(linetype = 3, size = 1, colour = "gray",
                 yintercept = 1:nlevels(dt_imp$variable)) +
  theme(text = element_text(family="Times"),
        panel.background = element_blank(), panel.grid = element_blank(),
        panel.border = element_rect(fill = NA), # legend.position = "none", 
        axis.title.x = element_text(family="sans", face = "bold", 
        vjust = -0.5, size = 12), 
        axis.text = element_text(family="sans",size = 11, 
                                 color = "black"), 
         legend.key = element_blank()) + 
        ylab("") + xlab("Percent Increase in Mean Square Error")
```
